Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection Fourier transform Mass Spectrometry Experiments

### 2022-04-15 doc/peakcharacterization_manuscript.Rmd
making sure figures get labeled

::: {custom-style="MDPI_5.2_figure"}
```{r coefficients_qcqa}
coef_df1 = data.frame(N_out = coefficients_qcqa$n_coef_out)
coef_g1 = coef_df1 %>%
  ggplot(aes(x = N_out)) + 
  geom_histogram() +
  labs(x = "# of Scan Outliers", y = "# of Samples")

@@

::: {custom-style="MDPI_5.2_figure"}
```{r resolution_qcqa}
tar_load(resolution_qcqa)

>>>>

::: {custom-style="MDPI_5.2_figure"}
```{r coefficients_qcqa, dn_id = figure_count}
coef_df1 = data.frame(N_out = coefficients_qcqa$n_coef_out)
coef_g1 = coef_df1 %>%
  ggplot(aes(x = N_out)) + 
  geom_histogram() +
  labs(x = "# of Scan Outliers", y = "# of Samples")

@@

::: {custom-style="MDPI_5.2_figure"}
```{r resolution_qcqa, dn_id = figure_count}
tar_load(resolution_qcqa)
